The hedging hyperprior for the exponential distribution

### 2024-06-20 text/23/exponential-hedging-hyperprior.Rmd
Update 2023 files

---
title: "The hedging hyperprior for the exponential distribution"
source: "New"
date: "2023-02-28"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
---

>>>>

---
title: "The hedging hyperprior for the exponential distribution"
source: "New"
date: "2023-02-28"
categories:
- Blog post
tags:
- Bayesian statistics
output: html_document
page_update: complete
---
